\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 related-work.tex
more on proof reuse and repair

\noindentparagraph{Proof reuse, proof weaving, and proof repair.}

\citet{boite2004proof} addresses proof reuse specifically in response
to inductive types extended with new constructors. Proof reuse is
via a tactic that adapts the original proof to the extended inductive
type while generating proof obligations, so rechecking of proof terms is
entailed.
The design requires distinct names for a base inductive type and its
extensions (including distinct names for constructors), while our
approach supports the late binding of names.

>>>>

\noindentparagraph{Proof reuse and proof repair.}

\citet{boite2004proof} addresses proof reuse specifically in response
to inductive types extended with new constructors. Proof reuse is
via a tactic that adapts the original proof to the extended inductive
type while generating proof obligations, so rechecking of proof terms is
entailed.
The design requires distinct names for a base inductive type and its
extensions (including distinct names for constructors), while family
polymorphism in our approach allows names to be late bound.

\citet{mulhern2006proof} introduces a heuristic approach that allows proofs
for multiple small languages to be combined to yield proofs for
composite languages, as long as the proof structure follows the same
pattern.
%
\citet{johlut2004} enable proof reuse in Isabelle by adapting theorems
from one setting for reuse in another: proof terms are transformed
by first explicitly stating all assumptions, and then abstracting over
function symbols and type constants.

Pumpkin Pi~\cite{ringer2021pumpkin} is a Coq plug-in that helps
repair proofs broken by changes in type definitions.
Its decompiler from proof terms to proof scripts prioritizes suggesting
useful tactics over soundness.
While Pumpkin Pi focuses on refactoring existing proofs in response to
changed definitions,
the focus of our solution is preempting refactoring altogether by
writing code that has built-in hooks for future extensions.
